Simple meta-analysis of survey data comparing different years is not possible based on a tremendous shift in the smartphone and mobile phone enviroemnt, this lead to the effect that the population changed and the gegenebenheiten

In this seciton we are going to analyse the research on data quality in smartphone web surveys. One has to differentiate between to effects. One is the mode effect of a web survey compared to other modes (CAPI, CATI etc). And then the effect of the device mobile versus pc (theoretically smartphonw versus tablet or feature phone). We will concentrate on the diffeerence on data quality between pc and smartphone in web survey. The intereseted reader can reffer to [citation] for a comparison of different modes. We will show the research fields in this and make an non quantiative summary of the most investigated items in data quality. 

There are various topics discussed in the reviewed paper, where 34 paper have data quality as a main topic. There already exist reviews to the data quality [citation]. We will update these review and complement them with this analysis. 

 'mobile design not optimized mobile avoid text answer more than optimized',
 'mobile design not optimized mobile completion time higher than optimized',
 'mobile design not optimized mobile less text than optimized',
 'mobile design not optimized mobile non substantial anwser more than optimized',
 mobile design optimized online higher completion rate
 mobile design optimized online higher completion rate

\begin{table}
	\centering
	\begin{tabular}{ll}
		\toprule
		Data Quality Topic  &  Research Articles \\
		\midrule
        mobile acquiescence more    & 0  \\
        mobile anwser changes more    & 0  \\
        mobile bias   & 0  \\
        mobile breakoff rate higher    & 0  \\
        mobile check all that apply anwsers less    & 0  \\
        mobile completion rate lower    & 0  \\
        mobile completion time higher    & 0  \\
        mobile construct validity    & 0  \\
        mobile device influence
        mobile enjoyment of survey less    & 0  \\
        mobile error rate higher    & 0  \\
        mobile estimates biased more    & 0  \\
        mobile inconsistent anwsers more    & 0  \\
        mobile instruction manipulation check failure more    & 0  \\
        mobile inter item correlation grid more    & 0  \\
        mobile lost focus more    & 0  \\
        mobile meaningfull answers less    & 0  \\
        mobile measurement quality lower    & 0  \\
        mobile midpoint responding more    & 0  \\
        mobile missing items rate higher    & 0  \\
        mobile more heaping    & 0  \\
        mobile more primacy    & 0  \\
        mobile more socially undesirables anwsers    & 0  \\
        mobile motivated underreporting more    & 0  \\
        mobile non differentiated answers more    & 0  \\
        mobile non substantial anwser more    & 0  \\
        mobile primacy effect higher    & 0  \\
        mobile reponse rate lower    & 0  \\
        mobile response time faster    & 0  \\
        mobile results different    & 0  \\
        mobile satisfaction lower    & 0  \\
        mobile satisficing check box more    & 0  \\
        mobile scale effects more    & 0  \\
        mobile sensitive questions answering less    & 0  \\
        mobile sensitive questions less sensitive    & 0  \\
        mobile socially undesirable answers more    & 0  \\
        mobile straightlining less    & 0  \\
        mobile technical difficulties more    & 0  \\
        mobile text answer avoid more    & 0  \\
        mobile text answer shorter    & 0  \\
        mobile text response nonrelevant more    & 0  \\
        mobile unaceptably short anwser less    & 0  \\
        mobile usability lower    & 0  \\
        mobile willingness rate lower & 0 \\
		\bottomrule 
	\end{tabular}
	\caption{Overview of the Professional Survey Operators used for more than one survey in the review}
	\label{tab: author}
\end{table}

There is a lot of research going on data quality as we could see in the previous table.. If we compare this with the quality indicators in (Citiation of an overview of data quality indicators) we see that currently research on is misisng. as this is more complciuated more sophistiacted tehcnolgies would need to be used. 

Our first research focus is the completion time of surves on mobile phones compared to pc. In 21 survey there was found statistical significant evidence, that completion time is longer on mobile devices compared to 8 surveys, that could not verify this hyptohesis. The evidence for longer completion time of survey on smartphone is therefore strong. An interesting observation however is that for all surveys, where we now if thes are optimized for mobile survey taking, the hypothesis was not verfiied. this coould be an indicator of an change if the surveys are better desinged for mobile first in this observation.

Secondly we will analysze the Breakoff rate of mobile surveys compared to PC surveys. We can see that 7 of 10 articles could validate the hypothesis that the breakoff rate is signficantly higher on a smartphone than on a pc. There were no obvious patterns of the survey setups that could not validate this hypothesis. So that we interpreate the evidence in this to be true. This can be explained with various theories [citation]. Aspect are that there is more multi tasking [citation], more deviations[cite]. The mobility [cite] and presence of other could also be an reason [cite] . Another theory could be the shorter attention span of mobile user [citation], that lead to faster frustration and therefore faster breakoff. Another important is the optimozation for mobile survey taking agian, since this has the potential to reduce the breakoff rate. 

As third point is the missing items. The hypotehsis we want to investigate is that the missing items rate is higher on surveys taken on smartphones than on pc. We found mixed evidence for this hypothesis as 5 times the hypothesis was not supported and 6 times the hypotheis was supported. An interesting pattern is seeable in the countries as we have countries likle Germany and Netherland were the hypothesis was both times two times validated countries like Spain and Netherlands where the hypothesis validated and not supported and in South Korea and and UK it was not supported. This could indicate an dependence on the country and mobile device sophisitication of the users. This hypothesis would need more support. This could be an research questions. 

Further analyses could be on
- Straightlining
- Primacy effect
- Non Substantial Answer
- Text Anwser


We have to view this results as temporary snapshot of the behavior, as our behaviour around mobile device is changing based on a rapidly developing development of the technology with ever new helps, large screen size and more learning effects for various groups (children, teenager, Adults, older population. As well as new design insights, that help to reduce the negative effext and coild also increase positive effects of mobile technologies.

One could go into more detailed in this section and do quantiatvie meta analysies to synthesize the different research results. This could be an future research endevaour. 
